### 2015-07-15 Docs/preface/preface.tex

\noindent The current version of the \maestro\ User's Guide can be found in 
the \maestro\ source tree under {\tt MAESTRO/docs/}.

\noindent Support is available via the mailing list: {\tt maestro-help@bender.astro.sunysb.edu}.  To subscribe to this list or read the archives, visit
\url{http://bender.astro.sunysb.edu/mailman/listinfo/maestro-help}.

>>>>

\noindent The current version of the \maestro\ User's Guide can be found in 
the \maestro\ source tree under {\tt MAESTRO/Docs/}.

\noindent Support is available via the mailing list: {\tt maestro-help@googlegroups.com}.  To subscribe to this list or read the archives, visit
\url{https://groups.google.com/forum/#!forum/maestro-help}.
